---
title: "Netflix Web Series Analysis Report"
author: "Group-21"
date: "`r Sys.Date()`"
output: html_document
knitr: 
  opts_chunk: 
    warning: FALSE
    message: FALSE
---

# Introduction

This report details the analysis of a dataset focusing on popular Netflix web series with ratings from Rotten Tomatoes. The analysis is based on a Shiny web app designed to explore various aspects of the data, including user ratings, critical scores, and genre distributions.

# a. Data Description

The dataset used for this project includes 10 popular Netflix series and contains the following columns:

-   **Title**: The name of the series.
-   **Genre**: The primary genre of the series (e.g., Drama, Crime, Sci-Fi).
-   **Tomatometer**: The percentage score from critics.
-   **Popcornmeter**: The percentage score from the audience.
-   **Seasons**: The number of seasons for each series.

**Dataset Size**: 10 observations, each representing a unique series.

# b. Obtaining the Data

The dataset was initially created as a demo with sample data hard-coded into the R code. The real application might involve data obtained through web scraping using `rvest` for ratings and other series details, or CSV imports for pre-collected data.

**Example data collection steps**: -

-   **Web scraping**: Used `rvest` to scrape show details and ratings from Rotten Tomatoes.

-   **CSV import**: Loaded locally stored data via `read.csv()`.

# c. Identifying Biases in the Data

Potential biases in the dataset include:

-   **Selection Bias**: The dataset represents only a select few popular series, omitting a comprehensive view of Netflix content.

-   **Recency Bias**: Series that recently gained popularity may be overrepresented.

-   **Rating Inconsistencies**: Audience and critic scores might not be fully representative due to limited samples or highly polarized reviews.

# d. Interesting Questions to Ask

-   Which genres have the highest critical acclaim (Tomatometer scores)?
-   Is there a correlation between Tomatometer and Popcornmeter scores?
-   Do series with more seasons tend to have higher audience engagement?
-   Which genre has the most consistent scoring patterns?
-   What is the distribution of ratings across different genres?

# e. Important Visualizations

### 1. Genre Distribution

```{r, echo=FALSE, include=TRUE}
# Create the data frame 
# set Working Directory.
data <- read.csv("data.csv") 
data$Tomatometer <- as.numeric(data$Tomatometer)
data$Popcornmeter <- as.numeric(data$Popcornmeter) 
data$Seasons <- as.numeric(data$Seasons)
```

# Plot 1: Genre distribution

```{r, echo=FALSE}
library(ggplot2)
ggplot(data, aes(x = Genre, fill = Genre)) +
  geom_bar(color = "black") + 
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Detailed Genre Distribution", x = "Genre", y = "Count") +  
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Plot 2: Tomatometer vs Audience Score

```{r, echo=FALSE}
library(ggplot2) 
ggplot(data, aes(x = Tomatometer, y = Popcornmeter, color = Genre)) +  
  geom_point(size = 4, alpha = 0.8) +  
  scale_color_brewer(palette = "Dark2") + 
  labs(title = "Tomatometer vs Audience Score", x = "Tomatometer Score (%)",y = "Audience Score (%)") + 
  theme_minimal(base_size = 16)
```

# Plot 3: Density plot

```{r, echo=FALSE}
library(ggplot2)
ggplot(data, aes(x = Tomatometer, fill = Genre)) + 
  geom_density(alpha = 0.6) + 
  scale_fill_brewer(palette = "Set3") +  
  labs(title = "Density of Tomatometer Scores by Genre", x = "Tomatometer Score (%)",y = "Density") +
  theme_minimal(base_size = 16)
```
